\ourlongtitle

### 2021-08-24 Bernoulli/AnswerReviews.tex

\begin{document}

\begin{center}
\textbf{Answer to Referees for \textit{"A pseudo-marginal sequential Monte Carlo online smoothing algorithm"}}
\end{center}

\bigskip

We would like to thank the associate editor and the referees for the attention they paid to our work and for their positive feedbacks.

@@

\medskip

{\bf p.7 Just before 2.2.2, it would be nice to comment on where one might get suitable adjustment weights $\vartheta_n$ from. How are these to be chosen or tuned?}\\
{\em To complete!}

\medskip

{\bf p.29 Appendix A in the supplement has $\phi_n(dx_n)[\ell(\cdot,x_{n+1})]$  in the numerator that arises from $B_n(x_{n+1},dx_n)$. I think this should read $\phi_n(dx_n)\ell(x_n,x_{n+1})$  instead?}\\
{\em The normalizing term given in the appendix is correct, see (2.10).}

@@

\medskip

{\bf p.30 Appendix A has $\phi_{0:n}L_{0,n}1_{X^n}$  in the denominator for  $\phi_{0:n+1}h$ which I think should read  $\phi_{0:n}L_{0,n}1_{X^{n+1}}$ as there is a dangling $dx_{n+1}$ otherwise.}\\
{\em There was indeed a mistake in this identity, thank you for pointing this out. This was corrected using (2.3).}

### 2021-08-24 Bernoulli/AnswerReviews.tex

We would like to thank the associate editor and the referees for the attention they paid to our work and for their positive feedbacks.

\bigskip

Minor errors and typos listed by R2 were corrected as suggested. Please find below a few detailed answers.

\begin{itemize}
\item p.7 (2.10) and elsewhere uses rectangular brackets as in $\phi_m[\ell_m(\cdot,x_{m+1})]$ which I think is meant to denote $\int_{X_m}\ell_m(x_m,x_{m+1})\phi_m(dx_m)$. This notation has not been introduced. The "Preliminaries" at the top of p.4 have $\mu h$ for the integral of a function $h$ against a measure $\mu$ which would suggest $\phi_m \ell(\cdot,x_{m+1})$. Since the rectangular brackets are used in this sense at many points in the paper, perhaps this notation should be added to the preliminaries.\\
{\em To do!}
\item p.7 Just before 2.2.2, it would be nice to comment on where one might get suitable adjustment weights $\vartheta_n$ from. How are these to be chosen or tuned?\\
{\em To do!}
\item p. 15-16: for the presentation of Example 2, I feel it would be better to describe the problem fully before giving Durham and Gallant's solution.\\
{\em Do not agree!}
\item p.29 Appendix A in the supplement has $\phi_n(dx_n)[\ell(\cdot,x_{n+1})]$  in the numerator that arises from $B_n(x_{n+1},dx_n)$. I think this should read $\phi_n(dx_n)\ell(x_n,x_{n+1})$  instead?\\
{\em The normalizing term given in the appendix is correct, see (2.10).}
\item p.30 Appendix A has $\phi_{0:n}L_{0,n}1_{X^n}$  in the denominator for  $\phi_{0:n+1}h$ which I think should read  $\phi_{0:n}L_{0,n}1_{X^{n+1}}$ as there is a dangling $dx_{n+1}$ otherwise.\\
{\em There was indeed a mistake in this identity, thank you for pointing this out. This was corrected using (2.3).}
\item It might have made the paper less scary and dry to read to first provide standard setups (along the lines of what is at the top of p.2), then proceed to the objective (formula (1.2)) and only then supplement all the measure-theoretic setup, e.g. as part of section 2. This would also have yielded the advantage of collecting mathematical notation at the start of section 2 (Is a collection of common notation in tabular form allowed in Bernoulli? This would be a friendly service to the reader.) rather than scattering it over the start of section 1 and section 2.\\
{\em To discuss!}
\end{itemize}

### 2021-08-24 Bernoulli/glo-2020-pm-PaRIS.tex
corrected typos (Bernoulli revision)

Let us turn our focus to backward sampling. As intractability of $\ud{n}$ implies intractability of the kernel $\trm{n}$ (defined in \eqref{eq:def:trm}), we aim at further pseudo marginalisation by embedding $\trm{n}$ into the extended kernel  
$$
\trmext{n}(i, j, \rmd z) \propto \ewght{n}{j} \ukest{n}{z}(\epart{n}{j}, \epart{n + 1}{i}) \, \ukdist{n}(\epart{n}{j}, \epart{n + 1}{i}, \rmd z)
$$
on $\intvect{1}{\N} \times \powerset{\intvect{1}{\N}} \tensprod \Zfd_{n + 1}$. For every $i$, the marginal of $\trmext{n}(i, \cdot)$ with respect to the $j$ component is, by \eqref{eq:def:udmod}, proportional to $\ewght{n}{j} \udmod{n}(\epart{n}{j}, \epart{n + 1}{i})$, a distribution that we expect to be close to $\trm{n}(i, \cdot)$ for small $\precpar$. The intractable sampling step on Line~3 in Algorithm~\ref{alg:ideal:BS} can therefore be replaced by sampling from $\trmext{n}(i, \cdot)$, after which the auxiliary variables are discarded. The latter sampling operation will be examined in detail in the next section. This approach, which we express concisely as 
$$
    (\tstat[i]{n + 1})_{i = 1}^\N \sim \mathsf{pmBS}((\epart{n}{i}, \tstat[i]{n}, \ewght{n}{i})_{i = 1}^\N, (\epart{n + 1}{i})_{i = 1}^\N), 
$$
is summarised in Algorithm~\ref{alg:pm:backward:sampling}.

@@

Assume that there exists some measurable nonnegative function $c$ on $\Xset_{n + 1}$ such that for all $(x_{n:n + 1}, z) \in \Xset_n \times \Xset_{n + 1} \times \Zset_{n + 1}$,
$
\ukest{n}{z}(x_n, x_{n + 1}) \leq c(x_{n + 1}).  
$
Since this condition allows the Radon--Nikodym derivative of $\trmext{n}(i, \cdot)$ with respect to the probability measure 
\begin{equation} \label{eq:proposal:pm:rejection}
\rho_n^i(j, \rmd z) \propto \ewght{n}{j} \kernel{R}(\epart{n}{j}, \epart{n + 1}{i}, \rmd z)
\end{equation} 
on $\powerset{\intvect{1}{\N}} \tensprod \Zfd_{n + 1}$ to be bounded uniformly as 
$$
\frac{\rmd \trmext{n}(i, \cdot)}{\rmd \rho_n^i}(j, z) \leq \frac{c(\epart{n + 1}{i}) \sumwght{n}}{\sum_{i' = 1}^\N \ewght{n}{i'} \udmod{n}(\epart{n}{i'}, \epart{n + 1}{i})},  
$$ 
we may sample from the target $\trmext{n}(i, \cdot)$ using rejection sampling. Thus, the following procedure is iterated until acceptance: simulate a candidate $(J^\ast, \zeta^\ast)$ from $\rho_n^i$ by drawing $J^\ast \sim \cat(\{ \ewght{n}{\ell} \}_{\ell = 1}^\N)$ and $\zeta^\ast \sim \kernel{R}(\epart{n}{J^\ast}, \epart{n + 1}{i}, \rmd z)$; then accept the same with (tractable) probability 
$$
\accprobext \eqdef \frac{\ukest{n}{\zeta^\ast}(\epart{n}{J^\ast}, \epart{n + 1}{i})}{c(\epart{n + 1}{i})}. 
$$ 
Then conditionally to acceptance, the candidate has distribution $\trmext{n}(i, \cdot)$.  
Notably, the probability $\accprobext$ is obtained by simply plugging a transition density estimate provided by \hypref{assum:biased:estimate} into the probability $\accprob$ (see \eqref{eq:std:acc:prob:backward:sampling}) corresponding to the case where $\ud{n}$ is known. Moreover, since the proposal density is independent of $i$, the expected complexity of this sampling schedule is linear in the number of particles (we refer again to \cite{douc:garivier:moulines:olsson:2010}).

>>>>

%Let us turn our focus to backward sampling. 
As intractability of $\ud{n}$ implies intractability of the kernel $\trm{n}$ (defined in \eqref{eq:def:trm}), we aim at further pseudo marginalisation by embedding $\trm{n}$ into the extended probability kernel  
$$
\trmext{n}(i, j, \rmd z) \propto \ewght{n}{j} \ukest{n}{z}(\epart{n}{j}, \epart{n + 1}{i}) \, \ukdist{n}(\epart{n}{j}, \epart{n + 1}{i}, \rmd z)
$$
on $\intvect{1}{\N} \times \powerset{\intvect{1}{\N}} \tensprod \Zfd_{n + 1}$. For every $i$, the marginal of $\trmext{n}(i, \cdot)$ with respect to the $j$ component is, by \eqref{eq:def:udmod}, proportional to $\ewght{n}{j} \udmod{n}(\epart{n}{j}, \epart{n + 1}{i})$, a distribution that we expect to be close to $\trm{n}(i, \cdot)$ for small $\precpar$. The intractable sampling step on Line~3 in Algorithm~\ref{alg:ideal:BS} can therefore be replaced by sampling from $\trmext{n}(i, \cdot)$, after which the auxiliary variables are discarded. The latter sampling operation will be examined in detail in the next section. This approach, which we express concisely as 
$$
    (\tstat[i]{n + 1})_{i = 1}^\N \sim \mathsf{pmBS}((\epart{n}{i}, \tstat[i]{n}, \ewght{n}{i})_{i = 1}^\N, (\epart{n + 1}{i})_{i = 1}^\N), 
$$
is summarised in Algorithm~\ref{alg:pm:backward:sampling}.

@@

Assume that there exists some measurable nonnegative function $c$ on $\Xset_{n + 1}$ such that for all $(x_{n:n + 1}, z) \in \Xset_n \times \Xset_{n + 1} \times \Zset_{n + 1}$,
$
\ukest{n}{z}(x_n, x_{n + 1}) \leq c(x_{n + 1}).  
$
Since this condition allows the Radon--Nikodym derivative of $\trmext{n}(i, \cdot)$ with respect to the probability measure 
\begin{equation} \label{eq:proposal:pm:rejection}
\rho_n^i(j, \rmd z) \propto \ewght{n}{j} \kernel{R}(\epart{n}{j}, \epart{n + 1}{i}, \rmd z)
\end{equation} 
on $\powerset{\intvect{1}{\N}} \tensprod \Zfd_{n + 1}$ to be bounded uniformly as 
$$
\frac{\rmd \trmext{n}(i, \cdot)}{\rmd \rho_n^i}(j, z) \leq \frac{c(\epart{n + 1}{i}) \sumwght{n}}{\sum_{i' = 1}^\N \ewght{n}{i'} \udmod{n}(\epart{n}{i'}, \epart{n + 1}{i})},  
$$ 
we may sample from the target $\trmext{n}(i, \cdot)$ using rejection sampling. Thus, the following procedure is iterated until acceptance: simulate a candidate $(J^\ast, \zeta^\ast)$ from $\rho_n^i$ by drawing $J^\ast \sim \cat(\{ \ewght{n}{j} \}_{j = 1}^\N)$ and $\zeta^\ast \sim \kernel{R}(\epart{n}{J^\ast}, \epart{n + 1}{i}, \rmd z)$; then accept the same with (tractable) probability 
$$
\accprobext \eqdef \frac{\ukest{n}{\zeta^\ast}(\epart{n}{J^\ast}, \epart{n + 1}{i})}{c(\epart{n + 1}{i})}. 
$$ 
Then conditionally to acceptance, the candidate has distribution $\trmext{n}(i, \cdot)$.  
Notably, the probability $\accprobext$ is obtained by simply plugging a transition density estimate provided by \hypref{assum:biased:estimate} into the probability $\accprob$ (see \eqref{eq:std:acc:prob:backward:sampling}) corresponding to the case where $\ud{n}$ is known. Moreover, since the proposal density is independent of $i$, the expected complexity of this sampling schedule is linear in the number of particles (we refer again to \cite{douc:garivier:moulines:olsson:2010}).
